SAT Solving for Vesicle Traffic Systems in Cells

### 2017-07-20 paper/experiments.tex
updated table2-description

%
We found no graph for the variant A with constraints Ann and Aen.
%
Replacing constraint on the node of Ann with Anb (variant B) does not affect the outcome.
%
If we allow every present molecule to stay active (Ann) but constraint the edge
by a boolean function (Aeb) the resultant VTS has to be at least 3-connected. Similarly, the results for the other cases are presented in the table. 
%
% If we constrain the activity of both the edge and the nodes with the boolean function (Anb and Aeb), 
% the VTS has to be 2-connected.
%
We ran experiments varying all parameters for specific N (size). For the comparison between both encodings (Table 2) we have fixed the total number of molecules to be twice as number of the nodes for N $>$ 2 and M = 2N + 1 for N = 2. For each version we also fix total number of parallel edges to maximum two. We have specifically chosen the same connectivity as Table 1 just for illustration purpose; for example in Table~\ref{tab:qf-grabh} Variant A, only check against graph with connectivity 2 is shown, in Variant B with connectivity 3 and similarly for the rest of the Variants.

@@

In Table~\ref{tab:qf-grabh}, we present the running times for the search of
VTSs of sizes 2 to 10 that satisfy the variants.
%
The experiments were done on a machine with Intel(R) Core(TM) i3-4030U
CPU @ 1.90GHz processor and 4GB RAM.
%
We have compared our performance with the performance of our earlier 
CBMC based implementation (old-encoding).
%
For example, the formula for variation F, the total number of
compartments ($|N|$) equals to 10, returns in 129.78 minutes (7786.8 secs)
with a SAT result.
%
In comparison, CBMC results in OUT OF MEMORY for $|N|$ greater than 5.
%
``!'' indicate that the constraints were unsatisfiable.
%
Using this encoding in comparison to the old one, not only we got efficiency improved for finding a SAT model but also did better in the case of refutation that no model exist (Table 2 variant A timing comparison and variant D with N =2). Hence with the use of this novel encoding, we are able to scale the system to a much larger compartmentalized system, especially to
eukaryotic cells with a total number of 10 compartments.
%
% \ankit{
% This additional scalability can provide us leverage to ask for related
% open questions that were not previously possible, for example, what is
% the minimum number of molecules required to satisfy the vesicular
% traffic system in eukaryotes.}
%
Furthermore, we experimented with limits of our tools and found
that $\zthree$ was able to solve the constraints up to $\sim{14-18}$ nodes.

>>>>

%
We found no graph for the variant A with constraints Ann and Aen.
%
Replacing constraint on the node of Ann with Anb (variant B) does not affect the outcome.
%
If we allow every present molecule to stay active (Ann) but constraint the edge
by a boolean function (Aeb) the resultant VTS has to be at least 3-connected. Similarly, the results for the other cases are presented in the table. 
%
% If we constrain the activity of both the edge and the nodes with the boolean function (Anb and Aeb), 
% the VTS has to be 2-connected.
%
We ran experiments varying all parameters for specific N (size). For the comparison between both encodings (Table 2) we have fixed the total number of molecules to be twice as number of the nodes for N $>$ 2 and M = 2N + 1 for N = 2. For each version we also fix total number of parallel edges to maximum two. We have specifically chosen the same connectivity as Table 1 just for illustration purpose; for example in Table~\ref{tab:qf-grabh} Variant A, only check against graph with connectivity 2 is shown, in Variant B with connectivity 3 and similarly for the rest of the Variants. Choice of Variants in the table reflects different type of results variations, for example we left out version B and E as it is of same connectivity type as of A \footnote{Complete result is present in our referenced repository}.

@@

In Table~\ref{tab:qf-grabh}, we present the running times for the search of
VTSs of sizes 2 to 10 that satisfy the variants.
%
The experiments were done on a machine with Intel(R) Core(TM) i3-4030U
CPU @ 1.90GHz processor and 4GB RAM.
%
We have compared our performance with the performance of our earlier 
CBMC based implementation (old-encoding).
%
For example, the formula for variation F, the total number of
compartments ($|N|$) equals to 10, returns in 129.78 minutes (7786.8 secs)
with a SAT result.
%
In comparison, CBMC results in OUT OF MEMORY for $|N|$ greater than 5.
%
``!'' indicate that the constraints were unsatisfiable.
%
Using this encoding in comparison to the old one, not only we got efficiency improved for finding a SAT model but also did better in the case of refutation that no model exist (Table 2 Variant A timing comparison and Variant D with N =2). Hence with the use of this novel encoding, we are able to scale the system to a much larger compartmentalized system, especially to
eukaryotic cells with a total number of 10 compartments.
%
% \ankit{
% This additional scalability can provide us leverage to ask for related
% open questions that were not previously possible, for example, what is
% the minimum number of molecules required to satisfy the vesicular
% traffic system in eukaryotes.}
%
Furthermore, we experimented with limits of our tools and found
that $\zthree$ was able to solve the constraints up to $\sim{14-18}$ nodes.
